Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd
Minor modifications

SampleID = SampleID %>%
  dplyr::select(SampleID, ID) %>%
  dplyr::mutate(ID = as.numeric(ID))

@@

# Get technical metadata
METADATA_ID <- 'syn5898489'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_ID
METADATA_TECHNICAL <- read.table(synGet(METADATA_ID)@filePath,sep='\t',header=T, row.names=1) %>%
  rownameToFirstColumn('OldBarcode')

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM36.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_36 =  BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID) %>%
  filter(!is.na(SampleID)) %>%
  filter(!(ID %in% c(335:341, 10567, 10622, 10577))) %>%
  unique
rownames(METADATA) = METADATA$SampleID

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=CDR, shape=SEX, size=PMI))
p <- p + theme_bw() + theme(legend.position="top") + scale_shape_manual(values = 1:7)
# p <- p + geom_text(aes(label= ID), size=4, hjust=1)
p

@@

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(Comparison, hgnc_symbol) %>%
  group_by(Comparison) %>%
  dplyr::summarise(nDiffExp = length(unique(hgnc_symbol)), 
                   DiffExpGenes = paste(unique(hgnc_symbol), collapse = ','))

kable(tmp)
```

>>>>

SampleID = SampleID %>%
  dplyr::select(SampleID, ID) %>%
  dplyr::mutate(ID = as.numeric(ID),
                Sample.ID = SampleID,
                SampleID = paste0('BM_36_',ID))

# Sum counts from multiple lanes
COUNT = dlply(SampleID, .(ID), .fun = function(x, count){
  rowSums(count[,x$Sample.ID,drop=F]) %>%
    rownameToFirstColumn('Gene.ID') %>%
    plyr::rename(c('DF' = paste0('BM_36_',unique(x$ID)))) %>%
    dplyr::select(-Gene.ID)
}, COUNT) %>%
  Reduce(cbind, .)
COUNT = data.matrix(COUNT)

@@

# Get technical metadata
METADATA_TECHNICAL_ID <- 'syn5898489'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_TECHNICAL_ID
METADATA_TECHNICAL <- read.table(synGet(METADATA_ID)@filePath,sep='\t',header=T, row.names=1) %>%
  rownameToFirstColumn('OldBarcode')

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM36.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_36 =  BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID %>% dplyr::select(-Sample.ID)) %>%
  filter(!is.na(SampleID)) %>%
  filter(!(ID %in% c(335, 338, 339, 341))) %>%
  unique
rownames(METADATA) = METADATA$SampleID

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=CDR, shape=SEX, size=PMI))
p <- p + theme_bw() + theme(legend.position="top") + scale_shape_manual(values = 1:7)
p <- p + geom_text(aes(label= ID), size=4, hjust=1)
p

@@

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(Comparison, hgnc_symbol) %>%
  group_by(Comparison) %>%
  dplyr::summarise(nDiffExp = length(unique(hgnc_symbol)), 
                   DiffExpGenes = paste(unique(hgnc_symbol), collapse = ','))
kable(tmp)
```
